\documentclass{resume}
\usepackage[left=0.65in,top=0.6in,right=0.65in,bottom=0.6in]{geometry}
\AtBeginEnvironment{itemize}{\setlength\parskip{0pt}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{}
\renewcommand\headrule{\makebox[\textwidth]{\rule{1.1\headwidth}{\headrulewidth}} \vskip-\headrulewidth}
\renewcommand\footrule{\makebox[\textwidth]{\rule{1.1\headwidth}{\headrulewidth}} \vskip-\headrulewidth}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}

\name{Qadis Chaudhry, EIT}
% \address{qadis.chaudhry@gmail.com \\ 917-702-4485 \\ github.com/QadisChaudhry \\ linkedin.com/in/QadisChaudhry}
\address{qadis.chaudhry@gmail.com \\ github.com/QadisChaudhry \\ linkedin.com/in/QadisChaudhry}

\begin{document}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

    \begin{rSection}{Experience}
        \begin{rSubsection}{Electrical Engineer}{Jul. 2024 - present}{Burns Engineering Inc.}{New York, New York}
            \item Aided a team of fifteen in the creation of design documents and the functional reports of eleven airports across the United States for United Airlines Full Electrification initiative.
            \item Composed single line diagrams and conducted site
                verifications for connections and metering, for the indexing of
                approximately ninety distribution substations located at
                Philadelphia International Airport.
        \end{rSubsection}
        \begin{rSubsection}{Electrical Design Associate}{May 2023 - May 2024}{Burns Engineering Inc.}{Philadelphia, Pennsylvania}
            \item Influenced construction and design of electrical systems
                and lighting coordination within new healthcare infrastructure
                consisting of over three hundred inpatient beds.
            \item Constructed and finalized plans for relocation of a power
                distribution system and the renewal of branch distribution
                systems within the major airport serving the city of
                Philadelphia.
        \end{rSubsection}
        \begin{rSubsection}{Software Development}{Feb. 2023 - May 2023}{Rutgers University}{New Brunswick, New Jersey}
            \item Coordinated a team of ten developers to create and launch a
                functioning web-based pharmaceutical delivery service catering
                to younger and older generations.
            \item Completed payment portal system and customer authorization
                and verification utilizing an external API fit to handle
                traffic of thousands of users simultaneously.
        \end{rSubsection}
        \begin{rSubsection}{Electrical Test Assistant}{Apr. 2021 - May 2023}{Alkhair Enterprises}{Haledon, New Jersey}
            \item Aided in the installation and operation of electrical
                equipment and machinery along with a group of five experienced
                tradesmen. Involved 0-1000 VAC motors and respective loads.
            \item Led effective solutions in the design process of electrical
                installations increasing production by 35\% and fostered aid in
                fabrication and troubleshooting.
        \end{rSubsection}
        \begin{rSubsection}{Virtual Machine Operator}{Jan. 2021 - Mar. 2021}{Self}{Monroe Township, New Jersey}
            \item Directed the installation and configuration of the five Linux
                operating system through the Unix command line for use of
                private individuals.
            \item Designed and committed a process for the troubleshooting and
                configuration of six different window managers.
                % to alleviate the need for command line use for the uninitiated.
        \end{rSubsection}
        \begin{rSubsection}{Development for Private Domain}{Apr. 2020 - Feb. 2021}{Self}{Monroe Township, New Jersey}
            \item Initiated and directed the creation of a software
                implementation to aid in a time sensitive operation to provide
                a competitive edge against thousands of users, whilst remaining
                undetectable.
            \item Developed three separate methods of automation and used
                concepts of HTTP requests, JavaScript, and JSON manipulation,
                to construct the program in Python for functional employment.
        \end{rSubsection}
        % \begin{rSubsection}{Lab Technician Assistant}{Jan. 2016 - Jun. 2018}{James Madison High School}{Brooklyn, New York}
        %     \item Facilitated the allowance of hands on analysis and configuration
        %         of laboratory experiments for available sections of chemistry,
        %         physics, and biology across four different grade levels.
        %     % \item Commanded the understanding and communication of each of the
        %     %     different materials, elements, and substances handled within the
        %     %     setting across each of the three domains.
        %     \item Coached the correct usage of materials for each of the lab
        %         experiments across the three domains consisting of greater than
        %         200 students altogether.
        % \end{rSubsection}
    \end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

    \vspace{-2mm}
    \begin{rSection}{Education}
        {\bf  Rutgers University - Graduate School of Engineering - Masters of Science} \hfill {\em Sept. 2024 - present} \\
        Specialization: Solid State Electronics and Systems and Controls \\
        {\bf Rutgers University - School of Engineering - Bachelors of Science} \hfill {\em Sept. 2020 - May 2024} \\
        Major: Electrical and Computer Engineering \\
        % Overall GPA: 3.8/4.0
        % \\
        % Relevant Coursework:
        %     Computer Architecture and Assembly Language,
        %     Principles of Electrical Engineering 1 \& 2,
        %     Digital Logic Design,
        %     Data Structures,
        %     Electromagnetic Fields,
        %     Linear Systems and Signals

        % {\bf High School}  \\
        % Monroe Township High School - Monroe Township, New Jersey \hfill {\em Sept. 2018 - Mar. 2020} \\
        % James Madison High School - Brooklyn, New York \hfill {\em Sept. 2016 - Jun. 2018}
        % \\
        % Relevant Coursework:
        %     Principles of Information Technology,
        %     Microsoft Certification,
        %     Computer Graphics Design,
        %     AP Computer Science Principles,
        %     AP Physics C (Mechanics and Electromagnetism)
    \end{rSection}
    \vspace{-2mm}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

    \begin{rSection}{Technical Strengths}
        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
            Languages &             Fluent: English, Urdu, Hindi, Punjabi; Partial: French, Arabic \\
            Engineering Design &    AutoCAD, Revit, AGI32, Cura, KiCAD, SPICE, PowerWorld Simulator \\
            % Machine Learning &      Neural Networks in Python, Evolution Algorithm in Processing \\
            % Markup Languages &      HTML, CSS, Markdown, and \LaTeX \\
            Programming &           Java, Python, JavaScript, MATLAB, C, C++ \\
            % Cloud Computing &     Experience with AWS (EC2 \& S3) \\
        \end{tabular}
    \end{rSection}
\end{document}
