\documentclass{resume}
\usepackage[left=0.65in,top=0.6in,right=0.65in,bottom=0.6in]{geometry}
\AtBeginEnvironment{itemize}{\setlength\parskip{0pt}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{}
\renewcommand\headrule{\makebox[\textwidth]{\rule{1.1\headwidth}{\headrulewidth}} \vskip-\headrulewidth}
\renewcommand\footrule{\makebox[\textwidth]{\rule{1.1\headwidth}{\headrulewidth}} \vskip-\headrulewidth}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}

\name{Qadis Chaudhry}
\address{qadis.chaudhry@gmail.com \\ 917-702-4485 \\ github.com/QadisChaudhry}

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
    % \begin{rSection}{Objective}
    %     A diligent and determined student working toward a degree in the field
    %     of engineering. A passion for theoretical as well as practical
    %     application, has allowed for constant curiosity to instantiate a life
    %     long pursuit of knowledge, not only in the world of today, but of the
    %     future as well.
    % \end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

    \begin{rSection}{Education}
        {\bf Rutgers University - School of Engineering} \hfill {\em Sept. 2020 - present} \\
        Major: Electrical and Computer Engineering \\
        Current Overall GPA: 3.808/4.0 \\
        Relevant Coursework:
            Computer Architecture and Assembly Language,
            Principles of Electrical Engineering 1 \& 2,
            Digital Logic Design,
            Intro. to Computers for Engineers (MATLAB)

        {\bf High School}  \\
        Monroe Township High School - Monroe Township, New Jersey \hfill {\em Sept. 2018 - Mar. 2020} \\
        James Madison High School - Brooklyn, New York \hfill {\em Sept. 2016 - Jun. 2018} \\
        Relevant Coursework:
            Principles of Information Technology,
            Microsoft Certification,
            Computer Graphics Design,
            AP Computer Science Principles,
            AP Physics C (Mechanics and Electromagnetism)
    \end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

    \begin{rSection}{Experience and Volunteering}
        \begin{rSubsection}{Virtual Machine Operator}{Jan. 2021 - Mar. 2021}{Administrator}{Monroe Township, New Jersey}
            \item Directed the installation and configuration of the Arch Linux
                operating system through the Unix command line on to three
                separate virtual machines for the use of a private individuals.
            \item Communicated the operation of two package managers, Homebrew and
                Pacman, to allow for the installation of needed firmwares and
                desired softwares in the future.
            \item Designed and committed a process for the trouble shooting and
                configuration of two different window managers, i3 and Xmonad,
                to alleviate the need for command line use for the uninitiated.
        \end{rSubsection}
        \begin{rSubsection}{Programming for Private Domain}{Apr. 2020 - Feb. 2021}{Lead Developer}{Monroe Township, New Jersey}
            \item Initiated and directed the creation of a program to aid in a
                weekly time sensitive operation where the program must be able
                to give a competitive edge, whilst remaining 100\% undetectable.
            \item Coordinated three different methods of automation and concepts of HTTP
                requests, JavaScript implementation, and JSON manipulation, to
                design and write the program in Python for functional employment.
        \end{rSubsection}
        \begin{rSubsection}{Lab Technician Assistant}{Jan. 2016 - Jun. 2018}{Assistant}{Brooklyn, New York}
            \item Facilitated the allowance of hands on analysis and configuration
                of laboratory experiments for available sections of chemistry,
                physics, and biology across four different grade levels.
            \item Commanded the understanding and communication of each of the
                different materials, elements, and substances handled within the
                setting across each of the three domains.
            \item Coached the correct usage of materials for each of the lab
                experiments across the three domains consisting of greater than
                200 students altogether.
        \end{rSubsection}
    \end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

    \begin{rSection}{Technical Strengths}
        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
            Languages & Fluent: English, Urdu, Hindi, Punjabi; Conversational: French, Arabic \\
            Visual Design & Adobe Illustrator and Photoshop, CAD, and CorelDRAW \\
            Machine Learning &  Neural Networks in Python, Evolution Algorithm in Processing \\
            Markup Languages &  HTML, CSS, Markdown, and \LaTeX \\
            Programming & Java, Python, JavaScript, MATLAB, C and C++ \\
            Cloud Computing & Experience with AWS (EC2 \& S3) \\
        \end{tabular}
    \end{rSection}
\end{document}
